---
title: "simulate_failure"
author: "Jirong"
date: "1 May 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Simulating product failures

I'm inspired by this post here (http://www.programmingr.com/examples/neat-tricks/sample-r-function/rexp/). And decided to expand on this example.

Say you are an owner of a computer store and you would like to estimate the cost of paying up on warranty repairs.

Here are the assumptions,
- Each computer is expected to last 7 years
- You only sell 1000 computers at the start of each year
- You sell computer up to 7th year


```{r}
set.seed(1) 
library(tidyr)

sim_repair_time = mapply(rexp, rep(1000, 7), rep(1/7, 7))
sim_repair_time = data.frame(sim_repair_time)
names(sim_repair_time) = paste0("Y", 2019:2025)
sim_repair_time$comp_index = 1:nrow(sim_repair_time)

sim_repair_time = sim_repair_time %>% gather(key = year, 
                                     value = spoilt_years_later, 
                                    -comp_index)
sim_repair_time$year = gsub("Y", "", sim_repair_time$year)
#sim_repair_time$spoilt_years_later = round(sim_repair_time$spoilt_years_later, 0)
sim_repair_time$year_spoilt = sim_repair_time$spoilt_years_later + as.numeric(sim_repair_time$year)

table(sim_repair_time$year_spoilt)
plot(table(sim_repair_time$year_spoilt))

#Tabulate number of 

```


## Explaining exponential distribution from first principle
$$f(x) =  {\lambda}e^{-\lambda x} $$

To understand pdf function here. It's pretty simple. If you run the simulator 1000 times with mean, lambda == 7. Then you plot the distribution, it's mostly likely front-loaded.

If you fit a series of values x to 1000 it will be pretty similar to simulated series of values.

And if you do a mean of the simulated data, it will return close to the mean

```{r}
data = rexp(1000, 1/7)
hist(data)
mean(data)
```





